---
title: "01-data-seahorses"
output: html_document 
---

## **Hippocampus reidi and where to see it in the wild**

The visable population and size of Hippocampus reidi will be compared to show where the most likely areas would be to see it 
in the wild. This can be used by snorkelers and skuba divers to plan
vacation destinations. 

In this document I will:

1.Import the dataset Hippocampus_reidi_Brazil.csv from the raw_data folder. 

2.Reduce the dataset down to pertanent information.

3.Dispay the information visually in a graph.

---

## Tourist locations for Hippocampus reidi in Brazil

## Required Packages

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

## Importing Data Set for Seahorses

```{r}
Hippocampus_reidi_Brazil <- read.csv("../raw_data/Hippocampus_reidi_Brazil.csv")
head(Hippocampus_reidi_Brazil)
```

## Narrowing Data Set to Relative Fields

```{r}
new_data <- select(Hippocampus_reidi_Brazil, Location, Number_Sighted, Average_Height_cm) 
   

knitr::kable(head(new_data))
```

## Plotting Average Height vs Number Sighted

```{r}
ggplot(data = new_data) + 
  geom_point(mapping = aes(x = Number_Sighted, y = Average_Height_cm, color = Location)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  xlab("Number Sighted") +
  ylab("Average Height (cm)") 
```



